---
title: "XPInfant `r sprintf('roi-%s',roi)`"
author: "Tomas Lenc"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pander)
library(doBy)
library(Rmisc)
library(plyr)
library(dplyr)
library(gtools)

library(ez)
library(lme4)
library(lmerTest)
library(car)
library(emmeans)
library(effectsize)

library(ggplot2)
library(cowplot)
library(colorspace)
library(ggnewscale)

# define functions 
source('utils.R')
```

```{r}
# define parameters
rm_sub <- c(1,14,15,16,18)

frex <- round(1/2.4 * c(2:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9,12), 3)

adjust_method = 'bonferroni'

# parameters for plotting 
cols <- c(low='#4000a6', high='#e0600f')
cols_individual <- lighten(cols, amount=0.7)
names(cols_individual) <- names(cols)
fontsize <-14

```

<br><br><br>

--- 

# Main analysis

```{r}
# load data
path_features <- file.path(experiment_path, sprintf('derivatives/features/features_roi-%s.csv', roi))
df_feat <- read.csv(path_features)
df_feat$subject <- factor(df_feat$subject)
df_feat$rhythm <- factor(df_feat$rhythm, levels=c('unsync','sync'))
df_feat$tone <- factor(df_feat$tone, levels=c('low','high'))

# remove bad subjects 
df_feat <- filter(df_feat, !subject%in%rm_sub)

```


```{r}
# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')

```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <- filter(data$meter, isMeterRel==TRUE)

```

```{r}
knitr::include_graphics(file.path(
    experiment_path, 
    'figures', 
    sprintf('roi-%s/roi-%s_summaryGrand_fftTypeEEG-amp_fftTypeCoch-amp.png', roi, roi)))
```


<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
p <- plot_amp_mean(df_amp_mean)
ggsave(file.path(reports_path, sprintf('roi-%s_ampMeanAll.pdf',roi)), p, width=4, height=2)
p
```

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% 
           filter(subject==2) %>% 
           dplyr::select(rhythm,tone,z_coch) %>% 
           mutate(z_coch=round(z_coch,2)),
       justify='left', 
       caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
p <- plot_z_meter(df_meterRel)
ggsave(file.path(reports_path, sprintf('roi-%s_zMeterRel.pdf',roi)), p, width=4, height=2)
p
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

<br> 

Compare mean z-score at meter-related frequencies in the EEG to zero, using one-sample t-test.  

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

<br> 

Compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br> 

Compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

Here the z-scores were taken using **decibels** in both EEG and cochlear model.  

```{r}
# test meter-rel zscore (eeg decibel) against cochlear model (power)
res <- ddply(df_meterRel, .(rhythm, tone), 
             function(df) tVsCoch(df, feature_eeg='z_eeg_db', feature_coch='z_coch_pow'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```

<br> 

Finally, we compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

Here the z-scores were taken using **decibels** in EEG and **power** in cochlear model.  

```{r}
# test meter-rel zscore against cochlear model (decibel)
res <- ddply(df_meterRel, .(rhythm, tone), 
             function(df) tVsCoch(df, feature_eeg='z_eeg_db', feature_coch='z_coch_db'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```







<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

```{r}
# t-test between normalized amplitude at meter-rel vs. undrelated frequencies
res <- ddply(df_meter, .(rhythm,tone), function(df) tMeterRelvsUnrel(df, feature='amp_eeg_norm'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test between normalized amplitude at meter-rel vs. undrelated frequencies. ')
```









<br><br>

## Meter amp (raw) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```

```{r}
# t-test between raw amplitude at meter-rel vs. undrelated frequencies
res <- ddply(df_meter, .(rhythm,tone), function(df) tMeterRelvsUnrel(df, feature='amp_eeg'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test between raw amplitude at meter-rel vs. undrelated frequencies. ')
```









<br><br><br>

--- 

# Control analysis (without 5Hz)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(2:11), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```

<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_coch) %>% mutate(z_coch=round(z_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
plot_z_meter(df_meterRel)
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <-ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```




<br><br><br>

--- 

# Control analysis (without 0.83Hz)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(3:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9,12), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```

<br><br>

<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_coch) %>% mutate(z_coch=round(z_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
plot_z_meter(df_meterRel)
```

```{r}
model <-ezANOVA(data=df_meterRel, dv=z_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```



<br><br><br>

--- 

# Control analysis (old orig selection)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(2:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,12), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```


<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <-ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_coch) %>% mutate(z_coch=round(z_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
plot_z_meter(df_meterRel)
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```





