---
title: "XPInfant `r sprintf('roi-%s',roi)`"
author: "Tomas Lenc"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pander)
library(doBy)
library(Rmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(gtools)

library(boot)
library(ez)
library(lme4)
library(lmerTest)
library(car)
library(emmeans)
library(effectsize)
library(Superpower)
library(pwr)

library(ggplot2)
library(cowplot)
library(colorspace)
library(ggnewscale)
library(gghalves)

# define functions 
source('utils.R')
```

```{r}
# define parameters
df_bad_sub <- read.csv(file.path(experiment_path, 'derivatives', 'bad_subjects.csv'))
rm_sub <- df_bad_sub$subject

frex <- round(1/2.4 * c(2:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9,12), 3)

adjust_method = 'bonferroni'

# parameters for plotting 
cols <- c(low='#4000a6', high='#e0600f')
cols_individual <- lighten(cols, amount=0.7)
names(cols_individual) <- names(cols)
fontsize <-14

```

<br><br><br>

--- 

# Main analysis


We will use the following frequencies of interest:  

```{r}
# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# load data
read_data <- function(data_path) {
    df <- read.csv(data_path)
    df$subject <- factor(df$subject)
    df$rhythm <- factor(df$rhythm, levels=c('unsync','sync'))
    df$tone <- factor(df$tone, levels=c('low','high'))
    return(df)
}

path_features <- file.path(experiment_path, sprintf('derivatives/features/features_roi-%s.csv', roi))
df_feat <- read_data(path_features)

# remove bad subjects 
df_feat <- filter(df_feat, !subject%in%rm_sub)

# load data from Lenc 2018
path_lowhigh <- file.path(experiment_path, 'code/experiment-lowhigh_features.csv')
df_feat_lowhigh <- read_data(path_lowhigh)

```

```{r}
# apply the current selection of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <- filter(data$meter, isMeterRel==TRUE)

# do the same for the data from Lenc 2018
data_lowhigh <- prepare_frex(df_feat_lowhigh, frex, frex_meterRel, feat_to_zscore=c('amp_eeg', 'amp_coch'))
df_meterRel_lowhigh <- filter(data_lowhigh$meter, isMeterRel==TRUE)
```

```{r}
knitr::include_graphics(file.path(
    experiment_path, 
    'figures', 
    sprintf('roi-%s/roi-%s_summaryGrand_fftTypeEEG-amp_fftTypeCoch-amp.png', roi, roi)))
```


<br><br>

## Overall response magnitude

Here we look at the overall magnitude of the EEG response. This is calculated by summing the FFT magnitudes across all frequencies of interest (i.e., irrespective of whether they are meter-related of -unrelated).  

```{r, fig.width=4, fig.height=2}
p <- plot_amp_mean(df_amp_mean)
ggsave(file.path(reports_path, sprintf('roi-%s_ampMeanAll.pdf',roi)), p, width=4, height=2)
p
```

Let's run an ANOVA with factors Tone and Rhythm.  

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```




<br><br>

## Meter zscore 

Next, we look at the relative prominence of meter-related frequencies. This is quantified by first z-scoring the FFT magnitudes across the frequencies of interest, and then averaging the z-score values across meter-related frequencies.   

Note that this way we obtain a relative measure of how much the meter-related frequencies stand out in the spectrum. That is, the z-scores at meter frequencies will be higher if (i) the raw amplitudes at meter-related frequencies get larger, and/or (ii) if the raw amplitudes at meter-unrelated frequencies get smaller. 

First, let's check the mete-related z-score taken from the spectra of the cochlear model.  

```{r}
pander(df_meterRel %>% 
           filter(subject==2) %>% 
           dplyr::select(rhythm,tone,z_amp_coch) %>% 
           mutate(z_amp_coch=round(z_amp_coch,2)),
       justify='left', 
       caption='Mean meter-related zscore for the cochlear model.')
```

<br> 

### Power analysis 

Before we get on with the analysis, let's justify the sample size.  

First, we use the same frequencies of interest as for the current study to re-analyze the data from Lenc 2018 (PNAS).  

We can start with the main comparison of the current study: testing whether there is selective neural enhancement of meter-related frequencies. To this end, we want to compare the compare mean z-score at meter-related frequencies in the EEG to cochlear model, using a one-sample t-test.  

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel_lowhigh, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```

We can take the mean effect size from Lenc 2018 across the high and low tone condition, and aim for 99% power.  


```{r}
d <- filter(res, rhythm=='sync') %>% select(cohens_d) %>% unlist() %>% mean()
pwr.t.test(d=d, power=0.99, sig.level=0.05, type='one.sample', alternative='greater')
```

<br> 

Next, we can look at the effect of tone frequency.  

```{r}
model <- ezANOVA(data=df_meterRel_lowhigh, dv=z_amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

Unlike in the original analysis, the interaction between rhythm and tone is only marginally significant when we use the current frequency selection (this is not surprising given the pvalue of 0.04 even in the original analysis that included the lowest frequency, i.e. 0.416 Hz).  

Hence, we will focus on the main effect of tone, which seems robust across analysis parameters.  

We use the data from Lenc 2018 to get parameters for power simulation with the [Superpower](https://aaroncaldwell.us/SuperpowerBook/) package.  

```{r, fig.width=4, fig.height=2}
df_wide <- df_meterRel_lowhigh %>% 
    pivot_wider(id_cols=subject, names_from=c(rhythm, tone), values_from=z_amp_eeg) %>%
    dplyr::select(!subject)

correlation_matrix <- cor(df_wide)
standard_deviations <- sapply(df_wide, sd)
means <- sapply(df_wide, mean)

# mean_sd <- mean(standard_deviations)
# mean_corr <- mean(correlation_matrix[row(correlation_matrix) < col(correlation_matrix)])

power_sim_design <- ANOVA_design(
    design='2w*2w',
    n=14,
    mu=means,
    sd=standard_deviations,
    r=correlation_matrix,
    label_list=list(rhythm=levels(df_meterRel_lowhigh$rhythm),
                     tone=levels(df_meterRel_lowhigh$tone))
)

```

```{r}
plot_power(power_sim_design, max_n=50, alpha_level=0.05, desired_power=80)
```








<br> <br> <br> 

---

### Infant data

Now let's move to the analysis of our EEG data.  

For the syncopated rhythm, meter zscore in the EEG was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_amp_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_amp_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
p <- plot_z_meter(df_meterRel)
ggsave(file.path(reports_path, sprintf('roi-%s_zMeterRel.pdf',roi)), p, width=4, height=2)
p
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```


<br> 

Just to check, let's run the same ANOVA using dB-normalized EEG spectra (note that this was a suggestion of Reviewer#2).  

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_db_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean dB zscore at meter-related frequencies.')
```





<br> 

Compare mean z-score at meter-related frequencies in the EEG to zero, using one-sample t-test.  

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

<br> 

Compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

This is the main analysis reported in the Results section.  

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br> 

Compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

This is a control analysis using the z-scores calculated after log transform of the spectra, i.e. from **decibels** in both EEG and cochlear model.  

```{r}
# test meter-rel zscore (eeg decibel) against cochlear model (power)
res <- ddply(df_meterRel, .(rhythm, tone), 
             function(df) tVsCoch(df, feature_eeg='z_db_eeg', feature_coch='z_pow_coch'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```

<br> 

Finally, we compare mean z-score at meter-related frequencies in the EEG to cochlear model, using one-sample t-test.  

This is a control analysis with z-scores taken using **decibels** in EEG and **power** in cochlear model.  

```{r}
# test meter-rel zscore against cochlear model (decibel)
res <- ddply(df_meterRel, .(rhythm, tone), 
             function(df) tVsCoch(df, feature_eeg='z_db_eeg', feature_coch='z_db_coch'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```







<br><br>

## Meter amp (normalized) 

To control for the role of normalization using z-scoring, let's run a 2x2x2 ANOVA (factors Rhythm, Tone, Meter) on amplitudes normalized between 0 and 1. We are looking for an interaction between Tone and Meter, in other words, the effect of Tone on the difference between normalized amplitudes at meter-related vs. -unrelated frequencies.   


```{r, fig.width=4.6, fig.height=4.2}
p <- plot_amp_meter(df_meter, col_name_eeg='amp_eeg_norm')
ggsave(file.path(reports_path, sprintf('roi-%s_ampNormMeter.pdf', roi)), p, width=4.6, height=4.2)
p
```

```{r, fig.width=3, fig.height=2}
p <- plot_amp_meter_diff(df_meter, col_name_eeg='amp_eeg_norm')
ggsave(file.path(reports_path, sprintf('roi-%s_ampNormMeterDiff.pdf', roi)), p, width=3, height=2)
p
```

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

```{r}
# t-test between normalized amplitude at meter-rel vs. unrelated frequencies
res <- ddply(df_meter, .(rhythm,tone), function(df) tMeterRelvsUnrel(df, feature='amp_eeg_norm'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,2,3,1), 
       caption='T-test between normalized amplitude at meter-rel vs. undrelated frequencies. ')
```









<br><br>

## Meter amp (raw) 

We can do the same as above, but without normalizing between 0 and 1, i.e. just by taking raw amplitudes in microV.  

```{r, fig.width=4.6, fig.height=4.2}
p <- plot_amp_meter(df_meter, col_name_eeg='amp_eeg')
ggsave(file.path(reports_path, sprintf('roi-%s_ampMeter.pdf', roi)), p, width=4.6, height=4.2)
p
```

```{r, fig.width=3, fig.height=2}
p <- plot_amp_meter_diff(df_meter, col_name_eeg='amp_eeg')
ggsave(file.path(reports_path, sprintf('roi-%s_ampMeterDiff.pdf', roi)), p, width=3, height=2)
p
```


```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```

```{r}
# break down interaction if present
if (res[res$Effect == 'rhythm:tone:isMeterRel', 'p'] < 0.05){
    model_unsync <- ezANOVA(data=filter(df_meter, rhythm=='unsync'),
                            dv=amp_eeg, wid=subject, within=.(tone,isMeterRel), return_aov=TRUE)
    res_unsync <- format_anova_table(model_unsync)
    pander(res_unsync, 
           justify='left',
           caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies (unsyncopated rhythm)')
}
```
```{r}
# break down further :)
if (res_unsync[res_unsync$Effect == 'tone:isMeterRel', 'p'] < 0.05){
    # t-test between raw amplitude for low vs. high (separate test for meter-rel vs. unrel freq)
    t <- ddply(filter(df_meter, rhythm=='unsync'),
                 .(isMeterRel), 
                 function(df) tLowVsHigh(df, feature='amp_eeg'))
    t$p <- p.adjust(t$p, method=adjust_method)
    t$signif <- stars.pval(t$p)
    
    pander(t, justify='left', digits=c(1,1,3,1,2,2,2,2,3,1), 
           caption='T-test between raw amplitude in low vs. high condition. (unsyncopated rhythm)')
}
```

```{r}
if (res[res$Effect == 'rhythm:tone:isMeterRel', 'p'] < 0.05){
    model_sync <- ezANOVA(data=filter(df_meter, rhythm=='sync'),
                            dv=amp_eeg, wid=subject, within=.(tone,isMeterRel), return_aov=TRUE)
    res_sync <- format_anova_table(model_sync)
    pander(res_sync, 
           justify='left',
           caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies (syncopated rhythm)')    
}
```


```{r}
# t-test between raw amplitude at meter-rel vs. undrelated frequencies
res <- ddply(df_meter, .(rhythm,tone), function(df) tMeterRelvsUnrel(df, feature='amp_eeg'))
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,2,2,2,3,1), 
       caption='T-test between raw amplitude at meter-rel vs. undrelated frequencies. ')
```









<br><br><br>

--- 

# Control analysis (without 5Hz)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(2:11), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```

<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_amp_coch) %>% mutate(z_amp_coch=round(z_amp_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_amp_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_amp_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
p <- plot_z_meter(df_meterRel)
ggsave(file.path(reports_path, sprintf('roi-%s_frex-without5_zMeterRel.pdf',roi)), 
       p, width=4, height=2)
p
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <-ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```




<br><br><br>

--- 

# Control analysis (without 0.83Hz)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(3:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,9,12), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```

<br><br>

<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <- ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_amp_coch) %>% mutate(z_amp_coch=round(z_amp_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_amp_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_amp_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
p <- plot_z_meter(df_meterRel)
ggsave(file.path(reports_path, sprintf('roi-%s_frex-without0.83_zMeterRel.pdf',roi)), 
       p, width=4, height=2)
p
```

```{r}
model <-ezANOVA(data=df_meterRel, dv=z_amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```



<br><br><br>

--- 

# Control analysis (old orig selection)

```{r}
# Define new selection of frequencies. 
frex <- round(1/2.4 * c(2:12), 3)
frex_meterRel <- round(1/2.4 * c(3,6,12), 3)

# print a table summarizing frequencies of interest
pander(get_frex_report(frex, frex_meterRel), caption='Frequencies of interest.')
```

```{r}
# apply the current selectino of meter-related/unrelated frequencies. 
data <- prepare_frex(df_feat, frex, frex_meterRel)
df_amp_mean <- data$mean_amp
df_meter <- data$meter
df_meterRel <-  filter(data$meter, isMeterRel==TRUE)
```


<br><br>

## Overall response magnitude

```{r, fig.width=4, fig.height=2}
plot_amp_mean(df_amp_mean)
```

```{r}
model <-ezANOVA(data=df_amp_mean, dv=amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean amplitude across all frequencies of interest (i.e. overall response magnitude).')
```


<br><br>

## Meter zscore 

```{r}
pander(df_meterRel %>% filter(subject==2) %>% dplyr::select(rhythm,tone,z_amp_coch) %>% mutate(z_amp_coch=round(z_amp_coch,2)), 
       justify='left', caption='Mean meter-related zscore for the cochlear model.')
```

For the syncopated rhythm, meter zscore was `r round(filter(df_meterRel,rhythm=='sync'&tone=='low')$z_amp_coch[1],3)` for the low tone and `r round(filter(df_meterRel,rhythm=='sync'&tone=='high')$z_amp_coch[1],3)` for the high tone. 

```{r, fig.width=4, fig.height=2}
plot_z_meter(df_meterRel)
```

```{r}
model <- ezANOVA(data=df_meterRel, dv=z_amp_eeg, wid=subject, within=.(rhythm,tone), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, justify='left',
       caption='ANOVA on mean zscore at meter-related frequencies.')
```

```{r}
# test meter-rel zscore against 0
res <- ddply(df_meterRel, .(rhythm,tone), tVs0)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against zero.')
```

```{r}
# test meter-rel zscore against cochlear model 
res <- ddply(df_meterRel, .(rhythm,tone), tVsCoch)
res$p <- p.adjust(res$p, method=adjust_method)
res$signif <- stars.pval(res$p)

pander(res, justify='left', digits=c(1,1,3,1,1,1), 
       caption='T-test of mean z-score at meter-related frequencies against cochlear model.')
```


<br><br>

## Meter amp (normalized) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg_norm, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean mean normalized amplitude (between 0-1) at meter-related vs. -unrelated frequencies.')
```

<br><br>

## Meter amp (raw) 

```{r}
model <- ezANOVA(data=df_meter, dv=amp_eeg, wid=subject, within=.(rhythm,tone,isMeterRel), return_aov=TRUE)
res <- format_anova_table(model)
pander(res, 
       justify='left',
       caption='ANOVA on mean raw amplitude at meter-related vs. -unrelated frequencies.')
```





